---
title: "Final Project R Reference"
author: "Alex Fink"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Reference Guide {.tabset .tabset-pills}

## Loading Data and Packages

```{r}
require(here)
require(palmerpenguins)
library(palmerpenguins)
```

```{r}
require(here)
ginkgo <- read.csv(here("data", "ginkgo_data_2021.csv"))
```



## Data Structures


### c()

The function c() combines or concatenates its arguments into a vector (a 1-dimensional data structure consisting of 1 or more elements).

* All of the elements must be of the same type.
* I can’t combine character and numeric types in the same call to c()

Here’s two examples using numeric and character data types:

```{r}
## Create a vector of numbers:
num_vec  = c(1, 4, 8, 9, 13)

## Create a vector of characters:
char_vec = c("a", "fish", "data is cool")

## Typing the name of the vector into the console prints the contents
num_vec

## The print() function accomplishes the same task:
print(char_vec)


```

### Length ()
* x -  an R object. For replacement, a vector or factor.
* value - a nn-negative integer or double (which will be rounded down).
```{r}
## Calculating the size of my vector

length(num_vec)

```
### matrix ()
* creates a matrix from the given set of values.
```{r}
vector1 = c(2,4,6,8,10,12)
matrix(data = 6, nrow = 3, ncol = 3)


```
### data.frame()
* couples variables which share similar properties of lists and matrices

```{r}
a = c(2)
b = c(4)
c = c(6)
df = data.frame(a,b,c)


```
 * Ginkgo Data
```{r}
nrow(ginkgo)
ncol(ginkgo)
dim(ginkgo)
```


## Subsetting
```{r}
ginkgo$notch_depth

```

```{r}
ginkgo_row_1 <- ginkgo[1,]
ginkgo_row_1
ginkgo_row_2_col_3 <- ginkgo[2,3]
ginkgo_row_2_col_3
ginkgo_col_3 <- ginkgo[,3]
ginkgo_col_3

```

```{r}
data_Adelie <- subset(penguins, species == "Adelie")
data_Adelie
```


## Numerical Data Exploration 
### summary
* Used to produce result summaries of the results of model fitting functions
```{r}
require(palmerpenguins)
head(penguins)
dat_penguins = data.frame(penguins)
summary(penguins)
```
### mean
* Function for the arithmetic mean
```{r}
mean(penguins$bill_depth_mm,na.rm = TRUE)
```
### sd()
* Computes the sd of the values of x
```{r}
sd(penguins$bill_depth_mm,na.rm = TRUE)
```

## Graphical Data Exploration 

### Scatterplot
```{r}
plot(max_width  ~ max_depth,data = ginkgo, xlab = "max_depth", ylab = "max_width", pch = 3, cex = 1.5, main = "ginkgo scatterplot", col = "blue", xlim = c(0,65), ylim = c(0,50))
     
```

```{r}

hist(penguins$flipper_length_mm , xlab = "flipper length", ylab = "frequency", main = "penguin flipper length histogram" ,col = "red", breaks = 12)
```

```{r}
boxplot(ginkgo$petiole_length, xlab = "petiole length", ylab= "frequency", main = "petiole length boxplot",col = "yellow")
```

```{r}
boxplot(max_depth~seeds_present, data = ginkgo,xlab = "max depth",ylab = "seeds present",main = "boxplot of seeds present", col = "green")
```
```{r}
par(mfrow = c(2,2))
    
hist(penguins$body_mass_g, xlab = "body mass", ylab = "frequency", main = "histogram of body mass", col = "purple")
hist(penguins$bill_depth_mm,xlab = "bill depth", ylab = "frequency", main = "histogram of bill depth", col = "brown")
hist(ginkgo$notch_depth,xlab = "notch depth", ylab = "frequency", main = "ginkgo notch depth", col = "green")
hist(ginkgo$petiole_length, xlab = "petiole length", ylab = "frequency", main = "histogram of petiole length", col = "red")

```

## Distribution Functions
```{r}
vector1 = c(2,4,6,8,10,12)
```

### dnorm()
```{r}
dnorm(3, 5, 0.5, log = FALSE)
```
### pnorm()
```{r}
pnorm(3, 5, 0.5, log = FALSE)
```
###qnorm()
```{r}
qnorm(0.8, mean = 50, sd = 1, lower.tail = TRUE, log.p = FALSE )
```
###dbinom
```{r}
dbinom(3, 5, 0.5, log = FALSE)
```
### pbinom()
```{r}
pbinom(3, 5, 0.5, log = FALSE)
```
### qbinom()
```{r}
qbinom(0.3, size =  5, prob = 0.5,lower.tail = TRUE, log.p = FALSE )
```




...